---
title: "Determinants of Youth Employment"
<<<<<<< HEAD
subtitle: "Sub-Saharan Africa"
=======
>>>>>>> a2be6e5a1950ec2ed6ab1c68204d3a5725180517
author: "Diego Del Pilar"
date: "December 4, 2019"
output: 
  beamer_presentation:
    theme: "AnnArbor"
    colortheme: "dolphin"
    fonttheme: "structurebold"
<<<<<<< HEAD
=======
    toc: true
>>>>>>> a2be6e5a1950ec2ed6ab1c68204d3a5725180517
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
<<<<<<< HEAD
setwd("~/")
library(haven)
library(sjlabelled)
library(tidyverse)
library(knitr)
library(xtable)
```

## Background
- Youth employment is a major concern in developing countries 
\vspace{0.5cm}
- Young people are up to 4x more likely than adults to be unemployed
\vspace{0.5cm}
- In developing countries, 85% of jobs taken by youth belong to informal markets
\vspace{0.5cm}
- A quarter of the young people cannot find a salary above extreme poverty line, $1.25 per day
\vspace{0.5cm}
- But youth are dissatisfied with their employment situation (rural & agricultural) and aspire to more 
\vspace{0.5cm}
=======
```

## Background
- Youth employment is a major concern of developing countries governments

- Young people are up to 4x more likely than adults to be unemployed

- In developing countries, 85% of jobs taken by Y belong to informal markets

- A quarter of the Y cannot find a salary above extreme poverty line, $1.25 per day

- But Y are dissatisfied with their employment situation (rural & agricultural) 

>>>>>>> a2be6e5a1950ec2ed6ab1c68204d3a5725180517
- Main reason for wanting to change: low pay, temporary nature of employment & poor working conditions 


## Problem statement
- Policy interventions from supply and demand side can be instrumented
<<<<<<< HEAD
\vspace{0.5cm}
- The International Labor Organization (ILO) designed the School-to-Work Transition Survey (SWTS):
  - Provide relevant labor market information on young people aged 15 to 29 years
  - Characteristics of youth
  - Characteristics of their jobs
  - Youth aspirations

## The data
- 2014 surveys for 9 Sub-Saharan Africa countries: Benin, Liberia, Togo, Congo, Malawi, Zambia, Madagascar, Tanzania and Uganda 
\vspace{0.5cm}
- Data wrangling: 
  - Each database is labeled differently
  - +400 questions per survey
  - Select variables of interest
  - Merge databases
\vspace{0.5cm}
- Started with 3 countries: Benin, Liberia, Togo. N size: 9,400

---
```{r include=FALSE}
library(rgdal)
my_spdf <- readOGR( 
  dsn= paste0(getwd(),"/Data/world_shape_file/") , 
  layer="TM_WORLD_BORDERS_SIMPL-0.3",
  verbose=FALSE
)
africa <- my_spdf[my_spdf@data$REGION==2 , ] 
par(mar=c(0,0,0,0))
```

## Africa plot

```{r africa}
# Plot africa
plot(africa , xlim=c(-50,10) , ylim=c(-50,35), col="steelblue", lwd=0.9 )
```

## 3. The model
The objective of the project is to find a model that predicts the probability of young people to find a job, base on certain characteristics, in Sub-Saharan Africa countries.

$$
\begin{aligned}
Y = \beta_{0} + \beta_{n} X_{n} + \epsilon
\end{aligned}
$$
Where: 
\vspace{0.5cm}

* $Y$ is the probability of a youth to being employed 
* $X_{n}$ is a matrix of predictors based on the information from the survey

## Logit regression
```{r include=FALSE}
# Databases are in stata

Togo_2014 <- read_dta("Data/Togo_2014.dta") %>%
  remove_all_labels(.)

Liberia_2014 <- read_dta("Data/Liberia_2014.dta") %>%
  remove_all_labels(.)

Benin_2014 <- read_dta("Data/Benin_2014.dta") %>%
  remove_all_labels(.)
```

```{r include=FALSE}
#Keeping just variables of interest and labeling
Benin_2014 <- select(Benin_2014, personid, m01_04, m01_07,m01_08, C05, C06,
                    C09, C10, C12, C14, C15, D01, E06, E07, E08, E10, E13J, 
                    E13K, E14Y, E17, E31, E37, F08, F19, F23, b06, b11n, b12,
                    b21, b23) %>%
  rename(
    id = personid,
    sex = m01_04,
    age = m01_07,
    married = m01_08,
    edu_level = C05,
    exp_level_edu = C06,
    ideal_work = C09,
    inter_school = C10,
    field_edu = C12,
    work_while_study = C14,
    intership = C15,
    employed = D01,
    where_work = E06,
    num_employ = E07,
    remuner = E08,
    type_contract = E10,
    social_security = E13J,
    train = E13K,
    salary = E14Y,
    salary_freq = E17,
    satisfaction = E31,
    union = E37,
    time_unemployed = F08,
    reserve_wage = F19,
    chall_job = F23,
    prev_resid = b06,
    child = b11n,
    financial_sit = b12,
    educ_fath = b21,
    educ_moth = b23
) %>%
  mutate(country = "Benin")

```

```{r include=FALSE}
#Creating an id
Togo_2014$id <- paste(Togo_2014$a8, Togo_2014$b1)

#Keeping just variables of interest and labeling
Togo_2014 <-select(Togo_2014, id, sex, age, b9, c5, c6, c9, c10, c12, c14, c15, d1,
                   e6, e7, E08, E10, e13j, e13k, e14b, payment_period, E31,
                   e37, f8, f19a, f23, b6, b11, b12, b21, b23) %>%
  rename(
    sex = sex,
    age = age,
    married = b9,
    edu_level = c5,
    exp_level_edu = c6,
    ideal_work = c9,
    inter_school = c10,
    field_edu = c12,
    work_while_study = c14,
    intership = c15,
    employed = d1,
    where_work = e6,
    num_employ = e7,
    remuner = E08,
    type_contract = E10,
    social_security = e13j,
    train = e13k,
    salary = e14b,
    salary_freq = payment_period,
    satisfaction = E31,
    union = e37,
    time_unemployed = f8,
    reserve_wage = f19a,
    chall_job = f23,
    prev_resid = b6,
    child = b11,
    financial_sit = b12,
    educ_fath = b21,
    educ_moth = b23
) %>%
  mutate(country = "Togo")
```

```{r include=FALSE}
base_merge <- rbind(Togo_2014, Benin_2014)
```

```{r include=FALSE}
#Creating a new unique id variable
Liberia_2014<- tibble::rowid_to_column(Liberia_2014, "id")

#Keeping just variables of interest and labeling
Liberia_2014 <-select(Liberia_2014, id, b4, b2, b9, c5, c6, c9, c10, c12, c14,
                      c15, d1, e6, e7, e8, e10, e13j, e13k, e14b, e17, e31, e37,
                      f8, f19, f23, b6, b11, b12, b21, b23) %>%
 rename(
    sex = b4,
    age = b2,
    married = b9,
    edu_level = c5,
    exp_level_edu = c6,
    ideal_work = c9,
    inter_school = c10,
    field_edu = c12,
    work_while_study = c14,
    intership = c15,
    employed = d1,
    where_work = e6,
    num_employ = e7,
    remuner = e8,
    type_contract = e10,
    social_security = e13j,
    train = e13k,
    salary = e14b,
    salary_freq = e17,
    satisfaction = e31,
    union = e37,
    time_unemployed = f8,
    reserve_wage = f19,
    chall_job = f23,
    prev_resid = b6,
    child = b11,
    financial_sit = b12,
    educ_fath = b21,
    educ_moth = b23
) %>%
  mutate(country = "Liberia")
```

```{r include=FALSE}
base_merge <- rbind(base_merge, Liberia_2014)
```

```{r include=FALSE}
base_merge$employed <- ifelse(base_merge$employed==1, 1, 0)
```

```{r echo=FALSE, warning=TRUE}
# Establish employed as a categorical variable
base_merge$employed <- factor(base_merge$employed)

mylogit <- glm(employed ~ sex + age + married + work_while_study + intership + child, data = base_merge, family = "binomial")

glm(employed ~ sex + age + married + work_while_study + intership + child, data = base_merge, family = "binomial") %>%
  summary() %>%
  xtable() %>%
  kable()
```

## Next steps
- Complete the data wrangling for the rest of the countries
- Machine learning techniques to find the best predictable model:
  - Logit with training and test data
  - K-Nearest Neighbors
  - Classification and Regression Trees (CART)
  - Random Forest
=======
- The International Labor Organization (ILO) designed the School-to-Work Transition Survey (SWTS):
  -Provide relevant labor market information on young people aged 15 to 29 years




## 3. Methods to use
Methods you explored or considered using.





## 4. Methods used so far
The methods/tools you used, and the rationale for their use.





## 5. Methods used so far
The methods/tools you used, and the rationale for their use.





## 6. Results
Show main visuals, analyses/tables, and/or any products built (interactive graphics,
websites, etc.)




## 7. Results
Show main visuals, analyses/tables, and/or any products built (interactive graphics,
websites, etc.)

>>>>>>> a2be6e5a1950ec2ed6ab1c68204d3a5725180517




<<<<<<< HEAD
=======
## 8. Results
Show main visuals, analyses/tables, and/or any products built (interactive graphics,
websites, etc.)





## 10. Lessons learned & plans to face challenges







## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```
>>>>>>> a2be6e5a1950ec2ed6ab1c68204d3a5725180517

