---
title: "Determinants of Youth Employment"
author: "Diego Del Pilar"
date: "December 4, 2019"
output: 
  beamer_presentation:
    theme: "AnnArbor"
    colortheme: "dolphin"
    fonttheme: "structurebold"
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Background
- Youth employment is a major concern of developing countries governments

- Young people are up to 4x more likely than adults to be unemployed

- In developing countries, 85% of jobs taken by Y belong to informal markets

- A quarter of the Y cannot find a salary above extreme poverty line, $1.25 per day

- But Y are dissatisfied with their employment situation (rural & agricultural) 

- Main reason for wanting to change: low pay, temporary nature of employment & poor working conditions 


## Problem statement
- Policy interventions from supply and demand side can be instrumented
- The International Labor Organization (ILO) designed the School-to-Work Transition Survey (SWTS):
  -Provide relevant labor market information on young people aged 15 to 29 years




## 3. Methods to use
Methods you explored or considered using.





## 4. Methods used so far
The methods/tools you used, and the rationale for their use.





## 5. Methods used so far
The methods/tools you used, and the rationale for their use.





## 6. Results
Show main visuals, analyses/tables, and/or any products built (interactive graphics,
websites, etc.)




## 7. Results
Show main visuals, analyses/tables, and/or any products built (interactive graphics,
websites, etc.)





## 8. Results
Show main visuals, analyses/tables, and/or any products built (interactive graphics,
websites, etc.)





## 10. Lessons learned & plans to face challenges







## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

